---
title: "tractR"
author: "Vikram Jambulapati"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tractR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

tractR provides a simple interface to interact with the U.S. Census Batch Geocoder. In particular, the U.S. Census Batch Gecoder restricts submissions to 10,000 addresses per call and requires addresses to be formatted in a particular order. tractR helps split your data into 10,000 address pieces and puts together the API call to the Geocoder.


## Example
tractR requires that your data contain the following elements: an identifier that uniquely identifies a row, street names, city, state and postal code. Let's use an example from public data.

```{r, include = FALSE}
# Load libraries for vignette
library(tractR)
library(httr)
library(data.table)
library(dplyr)
library(dtplyr)
library(pbapply)
library(stringr)
```

```{r, echo = FALSE, results = 'asis'}

CAMBRIDGE_URL <- 'https://data.cambridgema.gov/api/views/crnm-mw9n/rows.csv?accessType=DOWNLOAD&bom=true'
assessing     <- fread(CAMBRIDGE_URL, nrows = 10)
assessing$id  <- 1:nrow(assessing)
assessing$Zip <- str_pad(assessing$Zip, 5, pad = '0')
assessing     <- data.table(assessing)

assessing.geo <- getTracts(data       = assessing,
                           unique_id  = 'id',
                           address    = 'Mailing Address',
                           city       = 'City',
                           state      = 'State',
                           postalcode = 'Zip')
```


